---
title: "Covid-19 Acute Infection Test Performance"
author: "Blythe Adamson"
date: "12/31/2021"
output: html_document
---

__Date generated:__ `r format(Sys.time(), '%B %d, %Y')` 

__Author:__ Blythe Adamson


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning    = FALSE, 
                      message    = FALSE,
                      echo       = FALSE)
library(dplyr)
library(ggplot2)
library(xtable)
library(lubridate)
library(readr)
library(survival)
library(survminer)
```

```{r}
discordant_data <- read_csv("discordant_data.csv") 
```

## Viral Load Dynamics

The primary outcome of interest was concordance between PCR and rapid antigen test results, dependent on time and Ct values corresponding to infectiousness. 

```{r}
n_high_risk_day01 <- discordant_data %>% 
  filter(day == 0 | day == 1) %>% 
  group_by(flag_high_risk) %>% 
  summarise(n = n())
```

**Figure 1A.** Discordance in PCR and Antigen Rapid Test Results
```{r}

ag_discordant <- discordant_data %>% 
  filter(antigen == "Negative")

ag_concordant <- discordant_data %>% 
  filter(antigen == "Positive")

ag_missing <- discordant_data %>% 
  filter(is.na(antigen))

ggplot(discordant_data, aes(day, ct_saliva)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 29, ymax = Inf, 
           fill = "black", alpha = .1, color = NA) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 35, ymax = Inf, 
           fill = "black", alpha = .5, color = NA) +
  geom_line(aes(group = case), 
            alpha = .8,
            size = .6,
            color = "grey55",
            width = 0.2) +
  geom_point(data = ag_missing, aes(day, ct_saliva, 
                                    color = "Not Performed"), 
            alpha = .8,
            size = 1.5, 
            width = 0.2) +
  geom_jitter(data = ag_concordant, aes(day, ct_saliva, 
                                        color = "True Positive", 
                                        shape = manufacturer_ag), 
             size = 4,
             alpha = .8,
             width = 0.15,
             height = 0.2) +
  geom_jitter(data = ag_discordant, aes(day, ct_saliva, 
                                        color = "False Negative",
                                        shape = manufacturer_ag), 
             size = 4, 
             alpha = .8,
             width = 0.15,
             height = 0.2) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10),
                     limits = c(0, 10)) +
  xlab("Days from first positive test") +
  ylab("Saliva SARS-CoV-2 PCR Ct") +
  scale_y_reverse() +
  scale_color_manual(values = c("False Negative" = "orangered3", 
                                "True Positive" = "royalblue",
                                "Not Performed" = "grey55"),
                     name = "Antigen Test") +
  ylim(38,10) +
  scale_shape_manual(values=c(15, 17), name = "Manufacturer") +
  annotate("text", x = 9.5, y = 23.5, label = "Infectious") + 
  annotate("text", x = 9.5, y = 25, label = "Viral Load") + 
  annotate("text", x = 9.2, y = 33, label = "Not  Infectious") + 
  annotate("text", x = 9, y = 37, label = "PCR Negative", color = "white") + 
  theme_bw() +
  theme(axis.title.x = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 14))
```

## Kaplan Meier Analysis

A Kaplan Meier analysis was performed to estimate the median time from PCR positive to rapid antigen positive and time-dependent probability of a false negative rapid antigen test. We defined the index as the specimen collection date for the first PCR test with detectable SARS-CoV-2 with Ct <35, the event being the first positive rapid antigen test result, and censoring at the most recent antigen test date.

```{r}
tte <- discordant_data %>% 
  filter(antigen == "Positive") %>%
  group_by(case) %>% 
  filter(day == min(day)) %>% 
  select(case, day) %>% 
  mutate(event = 1) %>% 
  ungroup() %>% 
  distinct()

censor_time <- discordant_data %>% 
  filter(antigen != "Positive") %>%
  group_by(case) %>% 
  filter(day == max(day)) %>% 
  select(case, censor_day = day) %>% 
  ungroup() %>% 
  distinct()

concordant_tte <- discordant_data %>% 
  select(case) %>% 
  distinct() %>% 
  left_join(tte, by = "case") %>% 
  mutate(event = replace(event, is.na(event), 0)) %>% 
  left_join(censor_time, by = "case") %>% 
  mutate(tte = ifelse(event == 1, day, censor_day))
```

**Figure 1B.** Kaplan Meier Analysis of Time from PCR positive to Antigen Positive
```{r}
ggsurvplot(
    fit = survfit(Surv(tte, event) ~ 1, data = concordant_tte), 
    xlab = "Days from First PCR Positive Test", 
    ylab = "False-Negative Rapid Covid Ag (%)",
    conf.int = FALSE,
    legend = "none")
```

```{r}
surv_fit(Surv(tte, event) ~ 1,
               data = concordant_tte)
```

2022 INFECTIOUS ECONOMICS LLC
